\documentclass[12pt, notitlepage]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex

\usepackage{hyperref}

%Use for images
\usepackage{graphicx}
\graphicspath{ {./images/} }

%SetFonts

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}

%SetFonts

\title{
	\textbf{
		Mini-Quiz 8
	} \\
	\large BIOL 4301/6301 \\
	\large November 7, 2019 \\
}

\date{\vspace{-5ex}}

\def\wl{\par \vspace{\baselineskip}}

\begin{document}

{\fontfamily{phv}\selectfont %select helvetica (code = phv)

\large{Name:}

{\let\newpage\relax\maketitle}

\section{\small{Name an ecosystem process.}}

\wl
\wl
\wl
\wl

\section{\small{Name a state factor that controls ecosystem processes.}}

\wl
\wl
\wl
\wl

\section{\small{How do soils influence ecosystem processes?}}

\newpage

\section{\small{What is albedo?}}

\wl
\wl
\wl
\wl

\section{\small{How is energy absorbed at the Earth's surface partitioned?
Explain how this partitioning differs across ecosystems.}}

\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{\small{What are the primary components of a terrestrial ecosystem's water budget?}}

\newpage

\section{\small{What is the difference between gross primary productivity, net primary productivity,
and net ecosystem productivity?}}

\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{\small{What components of an ecosystem influence decomposition of organic material?}}

\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{\small{How does the nitrogen cycle differ from the phosphorus cycle?}}

\newpage

\section{\small{What is a keystone species?}}

\wl
\wl
\wl
\wl
\wl

\section{\small{How does biodiversity influence ecosystem services?}}

\wl
\wl
\wl
\wl
\wl

\section{\small{How could a disturbance preserve ecosystem functioning?}}

\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{\small{From the perspective of terrestrial ecosystem services, what
global change do you consider to be most important and why?}}


} %end font selection

\end{document}